Topic modeling on EU and the USA research projects

### 2017-06-24 thesis_report/draft_thesis.tex
Conclusion

>>>>

In this thesis, we have presented a work about discovering topics and their
trends in the field of scientific research. We applied the LDA model in projects
that got funded under the European Union Framework Programmes and the projects
funded by the National Science Foundation in the United States, for research and
innovation.

We briefly describe the preprocessing of the abstracts-documents before applying
the model. LDA, as an unsupervised learning algorithm, does not require any
prior annotation of labeling the documents and the topics are resulted from the
statistical structure of the words in the corpus. Using the posterior document-
topic and topic-word distribution, we investigate the context of each topic per
FP and the evolution of the topics in each of the two datasets over time.

We found that most topics cover various topics, while some show well-defined
scopes. Our work provides valuable knowledge about the research over the last
two decades in the two regions and could benefit researchers to to identify the
subjects that mostly get funded in the EU and USA. This research gives an
interesting aspect about what kind of topics were actually funded over the last
22 years.

The results of our research have several interesting insights that can make it
easier for people to understand the information contained in large datasets,
including extracting topics and their dynamics. The evolution of the topics over
time can also help researchers to find a set of promising topics to focus on and
start a project based on this knowledge. This could potentially increase their
chances to get a funding and have the opportunity to make their contribution in
scientific research.

Moreover, the information about what has been funded over the last years in
these two regions show that the scope of scientific research has become more
interdisciplinary and international as well. Even though we started analysing
the abstracts of the projects quantitatively, we also tried to discuss the
results and explain furtherthe evolution of the topics in research and potential
trends.

To sum up, discovering the topics in scientific research is a first step to
understand the knowledge that the research offers to the community in these two
regions, visualise the content and discover promising trends. We hore our work
could help people realise the potential of scientific research and inspire them
to identify meaningful topics to focus on.
